Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2024-01-05 article.tex
Insert flatten code

Building a graph is relatively straight forward, with the input for every function declared parsed as a tuple type named \mintinline{ocaml}{cfg}  of the form:
\begin{center}
\begin{minted}{ocaml}
type cfg = (lbl option * block) * (lbl * block) list
\end{minted}
\end{center}
which consists of an optionally named entry block in the first part and a list of trailing blocks that are always named in the second. The reason for the first block to be optionally named is the fact that \textit{some} LLVM programs transfer control back to the point of entry, whereas every subsequent block needs to be named because branching can only target it by its name.

From this, a CFG is constructed  using the \texttt{OCamlgraph} library \cite{ocamlgraph}, which provides several approaches with  various  structures, but the one used in this case is \texttt{Imperative.Digraph.Abstract} where the index is parameterized over \texttt{int} which corresponds to the index of the instruction starting at 0 for the first instruction to be executed. At first, a graph is constructed with the input flattened such that

@@

8 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01248x& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01766x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00146x& \cellcolor[rgb]{0.7548828125,0.9990234375,0.75} 1.02261x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00606x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01436x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99702x\\
10 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99586x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01369x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99508x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00861x& \cellcolor[rgb]{0.7548828125,0.9990234375,0.75} 1.01981x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00861x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02598x\\
12 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7548828125,0.9990234375,0.75} 1.02349x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04789x& \cellcolor[rgb]{0.759765625,0.9990234375,0.75} 1.04270x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03716x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06517x& \cellcolor[rgb]{0.763671875,0.9990234375,0.75} 1.05770x& \cellcolor[rgb]{0.77734375,0.9990234375,0.75} 1.11132x\\
14 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.759765625,0.9990234375,0.75} 1.04054x& \cellcolor[rgb]{0.763671875,0.9990234375,0.75} 1.05851x& \cellcolor[rgb]{0.759765625,0.9990234375,0.75} 1.04050x& \cellcolor[rgb]{0.7626953125,0.9990234375,0.75} 1.05301x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02863x& \cellcolor[rgb]{0.7607421875,0.9990234375,0.75} 1.04599x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16166x\\
16 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.771484375,0.9990234375,0.75} 1.08630x& \cellcolor[rgb]{0.7724609375,0.9990234375,0.75} 1.09112x& \cellcolor[rgb]{0.7666015625,0.9990234375,0.75} 1.06935x& \cellcolor[rgb]{0.7724609375,0.9990234375,0.75} 1.09077x& \cellcolor[rgb]{0.771484375,0.9990234375,0.75} 1.08669x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06631x& \cellcolor[rgb]{0.8525390625,0.9990234375,0.75} 1.41519x\\
18 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.7919921875,0.9990234375,0.75} 1.17172x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16684x& \cellcolor[rgb]{0.7880859375,0.9990234375,0.75} 1.15447x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16224x& \cellcolor[rgb]{0.7919921875,0.9990234375,0.75} 1.17110x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16144x& \cellcolor[rgb]{0.9560546875,0.9990234375,0.75} 1.83133x\\
20 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.806640625,0.9990234375,0.75} 1.23037x& \cellcolor[rgb]{0.80859375,0.9990234375,0.75} 1.23533x& \cellcolor[rgb]{0.8076171875,0.9990234375,0.75} 1.23433x& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.23986x& \cellcolor[rgb]{0.806640625,0.9990234375,0.75} 1.23120x& \cellcolor[rgb]{0.8046875,0.9990234375,0.75} 1.22283x& \cellcolor[rgb]{0.9990234375,0.990234375,0.75} 2.26430x\\
22 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30843x& \cellcolor[rgb]{0.8251953125,0.9990234375,0.75} 1.30498x& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30814x& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30594x& \cellcolor[rgb]{0.8251953125,0.9990234375,0.75} 1.30564x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29918x& \cellcolor[rgb]{0.9990234375,0.978515625,0.75} 2.64427x\\
24 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.8408203125,0.9990234375,0.75} 1.36606x& \cellcolor[rgb]{0.83984375,0.9990234375,0.75} 1.36299x& \cellcolor[rgb]{0.8408203125,0.9990234375,0.75} 1.36538x& \cellcolor[rgb]{0.83984375,0.9990234375,0.75} 1.36151x& \cellcolor[rgb]{0.83984375,0.9990234375,0.75} 1.36449x& \cellcolor[rgb]{0.83984375,0.9990234375,0.75} 1.36204x& \cellcolor[rgb]{0.9990234375,0.970703125,0.75} 2.89705x\\
26 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35207x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35059x& \cellcolor[rgb]{0.837890625,0.9990234375,0.75} 1.35397x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.34954x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35255x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.34932x& \cellcolor[rgb]{0.9990234375,0.9697265625,0.75} 2.92968x\\
28 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.8388671875,0.9990234375,0.75} 1.35918x& \cellcolor[rgb]{0.837890625,0.9990234375,0.75} 1.35626x& \cellcolor[rgb]{0.8388671875,0.9990234375,0.75} 1.36006x& \cellcolor[rgb]{0.837890625,0.9990234375,0.75} 1.35674x& \cellcolor[rgb]{0.8388671875,0.9990234375,0.75} 1.35812x& \cellcolor[rgb]{0.837890625,0.9990234375,0.75} 1.35462x& \cellcolor[rgb]{0.9990234375,0.96875,0.75} 2.96506x\\
30 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.8515625,0.9990234375,0.75} 1.41137x& \cellcolor[rgb]{0.8505859375,0.9990234375,0.75} 1.40745x& \cellcolor[rgb]{0.8515625,0.9990234375,0.75} 1.41125x& \cellcolor[rgb]{0.8505859375,0.9990234375,0.75} 1.40768x& \cellcolor[rgb]{0.8515625,0.9990234375,0.75} 1.40935x& \cellcolor[rgb]{0.8505859375,0.9990234375,0.75} 1.40589x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.08506x\\
32 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.853515625,0.9990234375,0.75} 1.41590x& \cellcolor[rgb]{0.8525390625,0.9990234375,0.75} 1.41255x& \cellcolor[rgb]{0.853515625,0.9990234375,0.75} 1.41652x& \cellcolor[rgb]{0.8525390625,0.9990234375,0.75} 1.41300x& \cellcolor[rgb]{0.8525390625,0.9990234375,0.75} 1.41399x& \cellcolor[rgb]{0.8515625,0.9990234375,0.75} 1.41115x& \cellcolor[rgb]{0.9990234375,0.9638671875,0.75} 3.09890x\\

@@

n & clang & greedy 12 & greedy 8 & greedy 6 & greedy 4 & greedy 2 & greedy 1 & greedy 0 & tiger \\

@@

8 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99429x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.98513x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00816x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01180x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99806x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00869x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00883x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99979x\\
10 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99057x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03464x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03147x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99206x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00151x& \cellcolor[rgb]{0.7607421875,0.9990234375,0.75} 1.04382x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04785x& \cellcolor[rgb]{0.763671875,0.9990234375,0.75} 1.05639x\\
12 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00006x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00578x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01540x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99370x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.97925x& \cellcolor[rgb]{0.7666015625,0.9990234375,0.75} 1.06915x& \cellcolor[rgb]{0.76953125,0.9990234375,0.75} 1.07918x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03213x\\
14 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02737x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02834x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04708x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02997x& \cellcolor[rgb]{0.7646484375,0.9990234375,0.75} 1.06066x& \cellcolor[rgb]{0.79296875,0.9990234375,0.75} 1.17635x& \cellcolor[rgb]{0.7841796875,0.9990234375,0.75} 1.14104x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12727x\\
16 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.771484375,0.9990234375,0.75} 1.08717x& \cellcolor[rgb]{0.7734375,0.9990234375,0.75} 1.09426x& \cellcolor[rgb]{0.77734375,0.9990234375,0.75} 1.11143x& \cellcolor[rgb]{0.7841796875,0.9990234375,0.75} 1.13760x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12774x& \cellcolor[rgb]{0.8525390625,0.9990234375,0.75} 1.41194x& \cellcolor[rgb]{0.849609375,0.9990234375,0.75} 1.40329x& \cellcolor[rgb]{0.8212890625,0.9990234375,0.75} 1.28770x\\
18 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12836x& \cellcolor[rgb]{0.7861328125,0.9990234375,0.75} 1.14704x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16301x& \cellcolor[rgb]{0.806640625,0.9990234375,0.75} 1.23098x& \cellcolor[rgb]{0.806640625,0.9990234375,0.75} 1.22815x& \cellcolor[rgb]{0.94140625,0.9990234375,0.75} 1.77085x& \cellcolor[rgb]{0.947265625,0.9990234375,0.75} 1.79503x& \cellcolor[rgb]{0.8720703125,0.9990234375,0.75} 1.49336x\\
20 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.806640625,0.9990234375,0.75} 1.22913x& \cellcolor[rgb]{0.8056640625,0.9990234375,0.75} 1.22392x& \cellcolor[rgb]{0.8173828125,0.9990234375,0.75} 1.27241x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35182x& \cellcolor[rgb]{0.845703125,0.9990234375,0.75} 1.38569x& \cellcolor[rgb]{0.9990234375,0.9912109375,0.75} 2.22689x& \cellcolor[rgb]{0.9990234375,0.990234375,0.75} 2.26200x& \cellcolor[rgb]{0.9501953125,0.9990234375,0.75} 1.80663x\\
22 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.822265625,0.9990234375,0.75} 1.29405x& \cellcolor[rgb]{0.8232421875,0.9990234375,0.75} 1.29616x& \cellcolor[rgb]{0.8349609375,0.9990234375,0.75} 1.34432x& \cellcolor[rgb]{0.865234375,0.9990234375,0.75} 1.46289x& \cellcolor[rgb]{0.8759765625,0.9990234375,0.75} 1.50765x& \cellcolor[rgb]{0.9990234375,0.98046875,0.75} 2.57480x& \cellcolor[rgb]{0.9990234375,0.9794921875,0.75} 2.62632x& \cellcolor[rgb]{0.9990234375,0.9970703125,0.75} 2.05105x\\
24 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.83203125,0.9990234375,0.75} 1.33240x& \cellcolor[rgb]{0.83203125,0.9990234375,0.75} 1.33275x& \cellcolor[rgb]{0.8486328125,0.9990234375,0.75} 1.39726x& \cellcolor[rgb]{0.87890625,0.9990234375,0.75} 1.52070x& \cellcolor[rgb]{0.892578125,0.9990234375,0.75} 1.57452x& \cellcolor[rgb]{0.9990234375,0.974609375,0.75} 2.77989x& \cellcolor[rgb]{0.9990234375,0.97265625,0.75} 2.83443x& \cellcolor[rgb]{0.9990234375,0.9931640625,0.75} 2.18442x\\

>>>>

Building a graph is relatively straight forward, with the input for every function declared parsed as a tuple type named \mintinline{ocaml}{cfg}  of the form:
\begin{minted}{ocaml}
type cfg = (lbl option * block) * (lbl * block) list
\end{minted}
which consists of an optionally named entry block in the first part and a list of trailing blocks that are always named in the second. The reason for the first block to be optionally named is the fact that \textit{some} LLVM programs transfer control back to the point of entry, whereas every subsequent block needs to be named because branching can only target it by its name.

From this, a CFG is constructed  using the \texttt{OCamlgraph} library \cite{ocamlgraph}, which provides several approaches with  various  structures, but the one used in this case is \texttt{Imperative.Digraph.Abstract} where the index is parameterized over \texttt{int} which corresponds to the index of the instruction starting at 0 for the first instruction to be executed. At first, a graph is constructed with the input flattened such that labels, instructions and terminators are represented as a contiguous sequence as opposed to the basic blocks that is parsed from the input.

\begin{minted}[bgcolor=LightGray]{ocaml}
let flatten ((head, tail) : Ll.cfg) : insn list =
  let label l = Label l and insn i = Insn i in
  let block (b : Ll.block) = List.map insn b.insns @ [ Term b.terminator ] in
  let named_opt (n, b) = (Option.map label n |> Option.to_list) @ block b in
  let named (n, b) = Label n :: block b in
  named_opt head @ (List.map named tail |> List.flatten)
\end{minted}

@@

8 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 139964& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00041x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.98897x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00518x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00397x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99405x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00683x& \cellcolor[rgb]{0.7548828125,0.9990234375,0.75} 1.02014x\\
10 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 141471& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00025x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00662x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00701x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.01013x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.01107x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99899x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03276x\\
12 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 143729& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01286x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00840x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02403x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.97714x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00222x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02376x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03188x\\
14 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 152717& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00032x& \cellcolor[rgb]{0.759765625,0.9990234375,0.75} 1.03967x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03472x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03637x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02969x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03224x& \cellcolor[rgb]{0.79296875,0.9990234375,0.75} 1.17572x\\
16 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 173395& \cellcolor[rgb]{0.76953125,0.9990234375,0.75} 1.08069x& \cellcolor[rgb]{0.7626953125,0.9990234375,0.75} 1.05265x& \cellcolor[rgb]{0.76953125,0.9990234375,0.75} 1.08045x& \cellcolor[rgb]{0.7705078125,0.9990234375,0.75} 1.08271x& \cellcolor[rgb]{0.7666015625,0.9990234375,0.75} 1.06793x& \cellcolor[rgb]{0.7666015625,0.9990234375,0.75} 1.06925x& \cellcolor[rgb]{0.8515625,0.9990234375,0.75} 1.40948x\\
18 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 227988& \cellcolor[rgb]{0.7890625,0.9990234375,0.75} 1.15964x& \cellcolor[rgb]{0.7880859375,0.9990234375,0.75} 1.15565x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16758x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16818x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16349x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16611x& \cellcolor[rgb]{0.951171875,0.9990234375,0.75} 1.80801x\\
20 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 375309& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.24200x& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.23989x& \cellcolor[rgb]{0.810546875,0.9990234375,0.75} 1.24662x& \cellcolor[rgb]{0.810546875,0.9990234375,0.75} 1.24412x& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.24000x& \cellcolor[rgb]{0.810546875,0.9990234375,0.75} 1.24497x& \cellcolor[rgb]{0.9990234375,0.990234375,0.75} 2.26177x\\
22 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 760328& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30708x& \cellcolor[rgb]{0.8271484375,0.9990234375,0.75} 1.31289x& \cellcolor[rgb]{0.8271484375,0.9990234375,0.75} 1.31045x& \cellcolor[rgb]{0.8271484375,0.9990234375,0.75} 1.31230x& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30795x& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30885x& \cellcolor[rgb]{0.9990234375,0.978515625,0.75} 2.63144x\\
24 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1763965& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35080x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35029x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35039x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35129x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35274x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.35185x& \cellcolor[rgb]{0.9990234375,0.97265625,0.75} 2.83868x\\
26 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 4321515& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.38984x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39041x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.38939x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39050x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39175x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39096x& \cellcolor[rgb]{0.9990234375,0.9677734375,0.75} 2.98115x\\
28 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 11291147& \cellcolor[rgb]{0.841796875,0.9990234375,0.75} 1.37185x& \cellcolor[rgb]{0.8427734375,0.9990234375,0.75} 1.37282x& \cellcolor[rgb]{0.8427734375,0.9990234375,0.75} 1.37280x& \cellcolor[rgb]{0.8427734375,0.9990234375,0.75} 1.37369x& \cellcolor[rgb]{0.8427734375,0.9990234375,0.75} 1.37371x& \cellcolor[rgb]{0.8427734375,0.9990234375,0.75} 1.37320x& \cellcolor[rgb]{0.9990234375,0.96875,0.75} 2.96675x\\
30 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 28225827& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.42877x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.42993x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.42896x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.43085x& \cellcolor[rgb]{0.857421875,0.9990234375,0.75} 1.43172x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.43069x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.09771x\\
32 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 73749658& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.43033x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.42973x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.42936x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.42954x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.43088x& \cellcolor[rgb]{0.8564453125,0.9990234375,0.75} 1.42974x& \cellcolor[rgb]{0.9990234375,0.9638671875,0.75} 3.10158x\\

@@

arg(s) & clang & greedy 12 & greedy 8 & greedy 6 & greedy 4 & greedy 2 & greedy 1 & greedy 0 & tiger \\

@@

8 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 139813& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99868x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00816x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00434x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00410x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01222x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00127x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01345x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01526x\\
10 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 141482& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99391x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.01001x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01231x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01469x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00529x& \cellcolor[rgb]{0.7548828125,0.9990234375,0.75} 1.02271x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03397x& \cellcolor[rgb]{0.7548828125,0.9990234375,0.75} 1.02248x\\
12 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 145091& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00774x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99627x& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01584x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.01047x& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01694x& \cellcolor[rgb]{0.7666015625,0.9990234375,0.75} 1.07056x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06622x& \cellcolor[rgb]{0.7607421875,0.9990234375,0.75} 1.04396x\\
14 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 149598& \cellcolor[rgb]{0.7646484375,0.9990234375,0.75} 1.06186x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06462x& \cellcolor[rgb]{0.7646484375,0.9990234375,0.75} 1.06184x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06665x& \cellcolor[rgb]{0.7705078125,0.9990234375,0.75} 1.08504x& \cellcolor[rgb]{0.7998046875,0.9990234375,0.75} 1.20101x& \cellcolor[rgb]{0.80078125,0.9990234375,0.75} 1.20679x& \cellcolor[rgb]{0.78515625,0.9990234375,0.75} 1.14215x\\
16 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 170028& \cellcolor[rgb]{0.7724609375,0.9990234375,0.75} 1.09372x& \cellcolor[rgb]{0.7734375,0.9990234375,0.75} 1.09738x& \cellcolor[rgb]{0.7802734375,0.9990234375,0.75} 1.12226x& \cellcolor[rgb]{0.783203125,0.9990234375,0.75} 1.13603x& \cellcolor[rgb]{0.7890625,0.9990234375,0.75} 1.15900x& \cellcolor[rgb]{0.85546875,0.9990234375,0.75} 1.42535x& \cellcolor[rgb]{0.857421875,0.9990234375,0.75} 1.43162x& \cellcolor[rgb]{0.8232421875,0.9990234375,0.75} 1.29614x\\
18 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 230073& \cellcolor[rgb]{0.7890625,0.9990234375,0.75} 1.15757x& \cellcolor[rgb]{0.7880859375,0.9990234375,0.75} 1.15498x& \cellcolor[rgb]{0.79296875,0.9990234375,0.75} 1.17517x& \cellcolor[rgb]{0.802734375,0.9990234375,0.75} 1.21433x& \cellcolor[rgb]{0.8134765625,0.9990234375,0.75} 1.25770x& \cellcolor[rgb]{0.93359375,0.9990234375,0.75} 1.73753x& \cellcolor[rgb]{0.947265625,0.9990234375,0.75} 1.79427x& \cellcolor[rgb]{0.876953125,0.9990234375,0.75} 1.51243x\\
20 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 376308& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.24275x& \cellcolor[rgb]{0.810546875,0.9990234375,0.75} 1.24539x& \cellcolor[rgb]{0.8193359375,0.9990234375,0.75} 1.28023x& \cellcolor[rgb]{0.837890625,0.9990234375,0.75} 1.35349x& \cellcolor[rgb]{0.8515625,0.9990234375,0.75} 1.41074x& \cellcolor[rgb]{0.9990234375,0.9912109375,0.75} 2.22527x& \cellcolor[rgb]{0.9990234375,0.990234375,0.75} 2.26082x& \cellcolor[rgb]{0.9521484375,0.9990234375,0.75} 1.81290x\\
22 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 762044& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30899x& \cellcolor[rgb]{0.826171875,0.9990234375,0.75} 1.30974x& \cellcolor[rgb]{0.8388671875,0.9990234375,0.75} 1.35873x& \cellcolor[rgb]{0.8623046875,0.9990234375,0.75} 1.45410x& \cellcolor[rgb]{0.8798828125,0.9990234375,0.75} 1.52442x& \cellcolor[rgb]{0.9990234375,0.98046875,0.75} 2.57640x& \cellcolor[rgb]{0.9990234375,0.9794921875,0.75} 2.62467x& \cellcolor[rgb]{0.9990234375,0.9970703125,0.75} 2.05193x\\
24 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1765499& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.34932x& \cellcolor[rgb]{0.8369140625,0.9990234375,0.75} 1.34929x& \cellcolor[rgb]{0.8505859375,0.9990234375,0.75} 1.40559x& \cellcolor[rgb]{0.876953125,0.9990234375,0.75} 1.51369x& \cellcolor[rgb]{0.896484375,0.9990234375,0.75} 1.59160x& \cellcolor[rgb]{0.9990234375,0.974609375,0.75} 2.78143x& \cellcolor[rgb]{0.9990234375,0.97265625,0.75} 2.83690x& \cellcolor[rgb]{0.9990234375,0.9931640625,0.75} 2.18519x\\
26 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 4399288& \cellcolor[rgb]{0.8408203125,0.9990234375,0.75} 1.36595x& \cellcolor[rgb]{0.8408203125,0.9990234375,0.75} 1.36628x& \cellcolor[rgb]{0.85546875,0.9990234375,0.75} 1.42456x& \cellcolor[rgb]{0.8837890625,0.9990234375,0.75} 1.53853x& \cellcolor[rgb]{0.904296875,0.9990234375,0.75} 1.62035x& \cellcolor[rgb]{0.9990234375,0.9716796875,0.75} 2.87046x& \cellcolor[rgb]{0.9990234375,0.9697265625,0.75} 2.92749x& \cellcolor[rgb]{0.9990234375,0.9912109375,0.75} 2.24179x\\
